PWD.KAZ

### 2019-07-17 results/PWD.KAZ.BivData.Rmd
work from home

@@

cells2curate <- KAZ_BivData_cells[KAZ_BivData_cells$pass_rate > .7,]

write.table(cells2curate, "~./MLH1repo/results/KAZ.cell.curate.csv", sep=",", row.names = FALSE)

@@

write.table(PWDcells2curate, "~./MLH1repo/results/PWD.cell.curate.csv", sep=",", row.names = FALSE)

@@

#pull all biv data for the full cell data
PWD_whole.cell.BivData <- PWD.Bivs.w.rank[PWD.Bivs.w.rank$fileName %in% PWDfull.cell.list$fileName,]
#ok these should be full cells
hist(hh2$rank, breaks =21)
#there are 2x as many 0's bc 1 and 0 are binned together
#update all hand.foci.counts
#y <- droplevels(y)

length.by.class <- ggplot(data=hh2, aes(x=fileName,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=hand.foci.count, shape=mouse))+ggtitle("PWD full cell SC lengths")
#most cells are from 1 mouse

@@

SC.test <- t.test()

@@

all.whole.cell <- rbind(KAZ_whole.cell.BivData,PWD_whole.cell.BivData)

>>>>

```{r}
#SC lengths by CO number

foci.pass <- KAZ_curate_BivData

@@

cells2curate <- KAZ_BivData_cells[KAZ_BivData_cells$pass_rate > .7,]
#write.table(cells2curate, "~./MLH1repo/results/KAZ.cell.curate.csv", sep=",", row.names = FALSE)

@@

#write.table(PWDcells2curate, "~./MLH1repo/results/PWD.cell.curate.csv", sep=",", row.names = FALSE)
```

@@

#pull all biv data for the full cell data
PWD_whole.cell.BivData <- PWD.Bivs.w.rank[PWD.Bivs.w.rank$fileName %in% PWDfull.cell.list$fileName,]
#ok these should be full cells

#there are 2x as many 0's bc 1 and 0 are binned together
#update all hand.foci.counts
#y <- droplevels(y)

#length.by.class <- ggplot(data=hh2, aes(x=fileName,y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=hand.foci.count, shape=mouse))+ggtitle("PWD full cell SC lengths")
#most cells are from 1 mouse

@@

#SC.test <- t.test()

```{r SC.Chrm, echo=FALSE}
all.curated.BivData <- rbind(KAZ.auto.man_BivData, PWD.auto.man_BivData)
all.whole.cell <- rbind(KAZ_whole.cell.BivData,PWD_whole.cell.BivData)

BivClass.SC_BivData <- ggplot(data=all.curated.BivData, aes(x=hand.foci.count,  y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=as.factor(hand.foci.count)))+ggtitle("PWD full cell SC lengths")+geom_boxplot(aes(alpha=.3))+facet_wrap(~strain)

BivClass.SC_whole.cell <- ggplot(data=all.whole.cell, aes(x=hand.foci.count,  y=chromosomeLength))+geom_jitter(width = 0.25, aes(color=as.factor(hand.foci.count)))+
  ggtitle("PWD full cell SC lengths")+
  geom_boxplot(aes(alpha=.3))+
  facet_wrap(~strain)

all.whole.cell.sub <- all.whole.cell[all.whole.cell$mouse != "18may15_PWD_m1",]

all.whole.cell.sub <- all.whole.cell.sub[all.whole.cell.sub$mouse != "6mar16_PWD_m1",]

all.whole.cell.sub <- all.whole.cell.sub[all.whole.cell.sub$hand.foci.count >= 1,]

table(all.whole.cell.sub$mouse)

SC.COnum <- ggplot(all.whole.cell.sub, aes(x=mouse, y=chromosomeLength, color=as.factor(hand.foci.count), fill=as.factor(hand.foci.count) ))+
  geom_jitter(alpha=0.8)+
  geom_boxplot(alpha=0.6) +theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  ggtitle("SC Length by Chromosome Class")+theme(legend.position="none")

@@
